%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.3, 10 May 2020) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

%% AltaCV uses the fontawesome5 and academicons fonts
%% and packages.
%% See http://texdoc.net/pkg/fontawesome5 and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the page layout if you need to
\geometry{left=1cm,right=1cm,top=1.25cm,bottom=1.25cm,columnsep=1cm}

% The paracol package lets you typeset columns of text in parallel
\usepackage{graphicx,wrapfig}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Roboto Slab}
  \setsansfont{Lato}
  \renewcommand{\familydefault}{\sfdefault}
\else
  % If using pdflatex:
  \usepackage[rm]{roboto}
  \usepackage[defaultsans]{lato}
  % \usepackage{sourcesanspro}
  \renewcommand{\familydefault}{\sfdefault}
\fi

% Change the colours if you want to
\definecolor{Black}{HTML}{000000}
% \definecolor{SlateGrey}{HTML}{2E2E2E}
% \definecolor{LightGrey}{HTML}{666666}
% \definecolor{DarkPastelRed}{HTML}{450808}
% \definecolor{PastelRed}{HTML}{8F0D0D}
% \definecolor{GoldenEarth}{HTML}{E7D192}
\colorlet{name}{black}
\colorlet{tagline}{Black}
\colorlet{heading}{Black}
\colorlet{headingrule}{Black}
\colorlet{subheading}{Black}
\colorlet{accent}{Black}
\colorlet{emphasis}{Black}
\colorlet{body}{Black}

% Change some fonts, if necessary
\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\footnotesize}
\renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}


% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{}

\name{Michal Skorczak}
\tagline{Software Engineer}
%% You can add multiple photos on the left or right
% \photoR{2.8cm}{Globe_High}
% \photoL{2.5cm}{Yacht_High,Suitcase_High}

\personalinfo{%
  % Not all of these are required!
  \email{mskorczak1@gmail.com}
  \homepage{mskorczak.xyz}
  \linkedin{mskorczak}
  \github{mskorczak}
  %You MUST add the academicons option to \documentclass, then compile with LuaLaTeX or XeLaTeX, if you want to use \orcid or other academicons commands.
  % \orcid{0000-0000-0000-0000}
  %% You can add your own arbtrary detail with
  %% \printinfo{symbol}{detail}[optional hyperlink prefix]
  % \printinfo{\faPaw}{Hey ho!}[https://example.com/]
  %% Or you can declare your own field with
  %% \NewInfoFiled{fieldname}{symbol}[optional hyperlink prefix] and use it:
  % \NewInfoField{gitlab}{\faGitlab}[https://gitlab.com/]
  % \gitlab{your_id}
}

\makecvheader

\cvsection{About Me}

Ambitious computer systems engineer graduate with a positive, proactive approach who excels at finding creative and efficient solutions. Driven to learn and possessing a strong worth ethic, with a desire to go above and beyond expectations.

\cvsection{Experience}

\cvevent{Software Developer}{Alan Blunden}{Jun 2022 -- Present}{Fully Remote - Southend-On-Sea, UK}
\begin{itemize}
	\item Developed and maintained existing, full-stack line of business applications for a variety of insurance brokers.
	\item Worked remotely as part of an agile team, collaborating and communicating with other teams in different disciplines.
	\item Used Azure Cloud technology to provide continous integration and delivery.
	\item Personally created a number of developer focused applications to make updating of insurance rules and rates easier.
	\item Maintained test suites for both front-end web and API applications.
\end{itemize}
\cvtag{PHP}
\cvtag{C\#}
\cvtag{Javascript}
\cvtag{Vue}
\cvtag{Python}
\cvtag{SQL}
\cvtag{Node.js}
\cvtag{JavaScript}
\cvtag{Git}
\cvtag{Windows}
\cvtag{Azure}

\divider

\cvevent{AV Technical Crew}{Students Union Essex University}{Sep 2021 -- Jun 2022}{Essex, UK}
\begin{itemize}
	\item Responsible for setting up various sound and lighting system for student events meeting optimal saftey standards.
	\item Worked on live events in technical, logistical and interpersonal aspects.
	\item Personally helped run a number of events for a number of different university societies (E-Sport tournaments, live music events).
\end{itemize}
\cvtag{Problem solving}
\cvtag{Teamwork}
\cvtag{Time Management}
\cvtag{Organisation}
\cvtag{Managment}
\cvtag{Logistics}
\cvtag{Health and Safety}
\cvtag{Audio Visual Technology}

\divider

\cvevent{Database Administrator}{TDP Marketing}{Dec 2018 -- Aug 2019}{Trimley St Mary, UK}
\begin{itemize}
	\item Provided marketing and sales data to businesses and consumers through managing various different databases.
	\item Created a variety of internal tools in order to increase efficiecy in retrieving and updating data and to comply with GDPR guidelines.
\end{itemize}
\cvtag{PHP}
\cvtag{JavaScript}
\cvtag{SQL}
\cvtag{HTML+CSS}
\cvtag{Windows}

\cvsection{Projects}

\cvevent{Panels}{Terminal User Interface}{April 2022 \github{mskorczak/panels}}{}

\begin{itemize}
	\item As part of my disertation (RISCV debugger) I wrote a simple terminal user interface, which has since been extended to support a number of different types of panels for displaying and interacting with a program.
\end{itemize}

\cvtag{C}
\cvtag{RISC-V Assembly}

\divider

\cvevent{Gibbon}{Hand Sign Trainer (Sign language and Naruto hand signs)}{April 2023 \github{mskorczak/gibbon}}{}

\begin{itemize}
	\item A hand sign trainer, built originally to train Naruto hand signs.
\end{itemize}

\cvtag{C++}
\cvtag{OpenCV}

%\divider
%
%\cvevent{Orn}{Sample transitioner for live music}{April 2023 \github{mskorczak/orn}}{}
%
%\begin{itemize}
%	\item A sample transitioner for live music, built for transitioning music for Dungeons and Dragons campaigns.
%\end{itemize}
%
%\cvtag{C++}
%
%\divider
%
%\cvevent{Pesterchum}{Instant Messaging Client/Server}{April 2023 \github{mskorczak/pesterchum}}{}
%
%\begin{itemize}
%	\item A Homestuck inspired instant messaging client/server combination.
%\end{itemize}
%
%\cvtag{IRC}
%
\cvsection{Education}

\cvevent{University Of Essex}{B.Eng in Computer Systemts Engineering}{2019 -- 2022}{Essex, UK}

\begin{itemize}
	\item Graduated with a 2.1, mentioned on the Deans list for excellence in all 3 years.
	\item Part of the Video Game, Game Development and Music Societies.
	\item Using my position as part of the AV Technical Crew, I helped run a number of events including a music festival 'Colch-ella' and the Derby Day 2022 E-Sports event.
\end{itemize}

\cvtag{Java}
\cvtag{C}
\cvtag{C++}
\cvtag{Python}

\divider

\cvevent{Suffolk One}{A Levels}{2017 -- 2019}{Ipswich, UK}

\begin{itemize}
	\item Completed my A Levels in Computer Science, Psychology and Mathematics
\end{itemize}

\cvsection{Skills}

\cvevent{Programming \& Other Languages}{}{}{}
\cvtag{C++}
\cvtag{C}
\cvtag{Python}
\cvtag{C\#}
\cvtag{Java}
\cvtag{JavaScript}
\cvtag{Bash}
\cvtag{GLSL}
\cvtag{Lua}
\cvtag{SQL}
\cvtag{HTML+CSS}
\cvtag{RISC-V Assembly}

\divider

\cvevent{Frameworks, Libs, \& Databases}{}{}{}
\cvtag{OpenGL}
\cvtag{SDL}
\cvtag{.NET}
\cvtag{Node.js}
\cvtag{NumPy}
\cvtag{OpenCV}

\divider

\cvevent{Development Tools \& Environment}{}{}{}
\cvtag{Git}
\cvtag{Linux}
\cvtag{GNU}
\cvtag{Visual Studio}
\cvtag{Neovim}
\cvtag{Suckless}

\cvsection{Others}

\cvachievement{\faIcon{map-marker-alt}}{National Citizenshup Service}{Helped build a sensory garden for the Ipswich Hospital as part of a social action project, involving the design, fundraising, logistics and manufacturing.}

\cvachievement{\faIcon{book}}{\href{https://cookbook.gg}{cookbook.gg}}{Did transcription work for Super Smash Bros. Melee 'tech'.}

\cvachievement{\faIcon{book}}{Languages}{Fluent in both Polish and English.}

% %% Yeah I didn't spend too much time making all the
% %% spacing consistent... sorry. Use \smallskip, \medskip,
% %% \bigskip, \vpsace etc to make ajustments.
% \medskip

\cvsection{References}

\cvref{Mathew Staples}{Line Manager - Alan Blunden}{mathew.staples-alanblunden.co.uk}
\cvref{Ben Wilson}{Head of Production - TDP Marketing}{benwilson@tdpmarketing.com}
\cvref{Callum Bartlett}{AV Technical Coordinator - Essex Students Union}{callum.bartlett@essex.ac.uk}
% \cvref{name}{email}{mailing address}
% \cvref{Prof.\ Alpha Beta}{Institute}{a.beta@university.edu}
% {Address Line 1\\Address line 2}

% \divider

More available upon request.

\end{document}
